\thetitle

### 2008-06-14 paper.tex
New subtitle.
More work on appearance of models table.

\newcommand{\thetitle}{Linear Representation of Network Traffic}
\newcommand{\thesubtitle}{With Applications to Generating Realistic Wireless Workload}
\newcommand{\theauthors}{
  Stefan~Karpinski \and
  Elizabeth~M.~Belding \and
  Kevin~C.~Almeroth \and
  John~R.~Gilbert
}

\usepackage[labelfont=bf,small]{caption}
\usepackage[font=small,labelfont=bf,position=top,nearskip=0em]{subfig}
\usepackage{cite,amsmath,amssymb,rotating,multirow,bigstrut,url,wrapfig,relsize,paralist,array,mathtools}
\usepackage[hyperfigures,bookmarks,bookmarksopen,bookmarksnumbered,colorlinks,linkcolor=black,citecolor=black,filecolor=blue,menucolor=black,pagecolor=blue,frenchlinks=true,pdftitle={\thetitle: \thesubtitle}]{hyperref}

@@

From the matrices $\mat{Z}$ and $\mat{V}$ we can compute a variety of statistics about packet sizes and inter-packet intervals.
The flows vectors in the matrices may represent individual flows or composites of many flows.
% about packet sizes, total packet count, inter-packet intervals, and total duration for each representation vector, which may represent a single actual flow, or the composite behavior of many flows.
% We begin by expressing the vectors for total bytes, total packets and total duration for a matrix of flow representations, with size and interval matrices $\mat{Z}$ and $\mat{V}$.
The computations require knowing the values that each size of interval matrix column represents.
% The computed duration is approximate because information is irretrievably lost in the quantization process.
The vectors of representative values for $\mat{Z}$ and $\mat{V}$ respectively are:
\begin{align}
\vec{\sigma} &= \tuple{1,2,3,\dots,d_z} \\
\vec{\tau}   &= \tuple{\Df_\ival\left(k-\fracx{1}{2}\right)}_{k=1}^{d_v}.
\end{align}
The packet count, total byte and total duration vectors are computed as
\begin{align}
\vec{\Sigma}_\pkts  &= \mat{Z}\trans{\ones} = \mat{V}\trans{\ones} \in \R^f \eqn{packet-count}\\
\vec{\Sigma}_\bytes &= \mat{Z}\trans{\vec{\sigma}} \in \R^f \eqn{total-bytes} \\
\vec{\Sigma}_\ivals &= \mat{V}\trans{\vec{\tau}} \in \R^f \eqn{total-duration}.
\end{align}
Here $\ones$ is a row vector of all ones.\onesnote
Packet count and total bytes values are exact;
the total durations are only approximate because information is irretrievably lost in the quantization process.
Using these vectors of totals, we may readily compute the average packet sizes and inter-packet intervals:
\begin{align}
\vec{\mean{z}} &=
  \vec{\Sigma}_\bytes \eldiv \vec{\Sigma}_\pkts
  \phantom{= \mat{V}\trans{\vec{\tau}} \eldiv \mat{V}\trans{\ones}}
  \mathllap{= \mat{Z}\trans{\vec{\sigma}} \eldiv \mat{Z}\trans{\ones}} \\
\vec{\mean{v}} &=
  \phantom{\vec{\Sigma}_\bytes \eldiv \vec{\Sigma}_\pkts}
  \mathllap{\vec{\Sigma_{\ivals}} \eldiv \vec{\Sigma_{\pkts}}}
  = \mat{V}\trans{\vec{\tau}} \eldiv \mat{V}\trans{\ones}.
\end{align}
The symbol $\eldiv$ here represents element-wise division of vector coordinates, as it does in Matlab.

@@

The \caps{GMM} has the benefit of making the conditioning of behaviors completely explicit. It also allows us to easily define intermediate choices. If we wish make the behavior of each flow a weighted average of the composite behaviors of its source and destination nodes, we can express this easily:
\begin{align}
\mat{F}' = ((1-\alpha)\,\rStoch(\trans{\mat{S}}\mat{S})+(\alpha)\,\rStoch(\trans{\mat{D}}\mat{D}))\mat{F}.
\end{align}
The parameter $\alpha$ allows us to smoothly vary the weighting of the source and destination behaviors. Source-only behavior is given by $\alpha=0$; destination-only by $\alpha=1$; to weight source and destination equally, take $\alpha=\frac{1}{2}$.

>>>>

\newcommand{\thetitle}{Linear Representation of Network Traffic}
\newcommand{\thesubtitle}{With Special Application to Wireless Workload Generation}
\newcommand{\theauthors}{
  Stefan~Karpinski \and
  Elizabeth~M.~Belding \and
  Kevin~C.~Almeroth \and
  John~R.~Gilbert
}

\usepackage[labelfont=bf,small]{caption}
\usepackage[font=small,labelfont=bf,position=top,nearskip=0em]{subfig}
\usepackage{cite,amsmath,amssymb,rotating,multirow,bigstrut,url,wrapfig,relsize,paralist,array,mathtools,units}
\usepackage[hyperfigures,bookmarks,bookmarksopen,bookmarksnumbered,colorlinks,linkcolor=black,citecolor=black,filecolor=blue,menucolor=black,pagecolor=blue,frenchlinks=true,pdftitle={\thetitle: \thesubtitle}]{hyperref}

@@

From the matrices $\mat{Z}$ and $\mat{V}$ we can compute a variety of statistics about packet sizes and inter-packet intervals.
The flows vectors in the matrices may represent individual flows or composites of many flows.
% about packet sizes, total packet count, inter-packet intervals, and total duration for each representation vector, which may represent a single actual flow, or the composite behavior of many flows.
% We begin by expressing the vectors for total bytes, total packets and total duration for a matrix of flow representations, with size and interval matrices $\mat{Z}$ and $\mat{V}$.
The computations require knowing the values that each size of interval matrix column represents.
% The computed duration is approximate because information is irretrievably lost in the quantization process.
The vectors of representative values for $\mat{Z}$ and $\mat{V}$ respectively are:
\begin{align}
\vec{\sigma} &= \tuple{1,2,3,\dots,d_z} \\
\vec{\tau}   &= \tuple{\Df_\ival\left(k-\fracx{1}{2}\right)}_{k=1}^{d_v}.
\end{align}
The packet count, total byte and total duration vectors are computed as
\begin{align}
\vec{\Sigma}_\pkts  &= \mat{Z}\trans{\ones} = \mat{V}\trans{\ones} \in \R^f \eqn{packet-count}\\
\vec{\Sigma}_\bytes &= \mat{Z}\trans{\vec{\sigma}} \in \R^f \eqn{total-bytes} \\
\vec{\Sigma}_\ivals &= \mat{V}\trans{\vec{\tau}} \in \R^f \eqn{total-duration}.
\end{align}
Here $\ones$ is a row vector of all ones.\onesnote
Packet count and total bytes values are exact;
the total durations are only approximate because information is irretrievably lost in the quantization process.
Using these vectors of totals, we may readily compute the average packet sizes and inter-packet intervals:
\begin{align}
\vec{\mean{z}} &=
  \vec{\Sigma}_\bytes \eldiv \vec{\Sigma}_\pkts
  \phantom{= \mat{V}\trans{\vec{\tau}} \eldiv \mat{V}\trans{\ones}}
  \mathllap{= \mat{Z}\trans{\vec{\sigma}} \eldiv \mat{Z}\trans{\ones}} \\
\vec{\mean{v}} &=
  \phantom{\vec{\Sigma}_\bytes \eldiv \vec{\Sigma}_\pkts}
  \mathllap{\vec{\Sigma_{\ivals}} \eldiv \vec{\Sigma_{\pkts}}}
  = \mat{V}\trans{\vec{\tau}} \eldiv \mat{V}\trans{\ones}.
\end{align}
The symbol $\eldiv$ here represents element-wise division of vectors, as it does in Matlab.

@@

The \caps{GMM} has the benefit of making the conditioning of behaviors completely explicit. It also allows us to easily define intermediate choices. If we wish make the behavior of each flow a weighted average of the composite behaviors of its source and destination nodes, we can express this easily:
\begin{align}
\mat{F}' = ((1-\alpha)\,\rStoch(\trans{\mat{S}}\mat{S})+(\alpha)\,\rStoch(\trans{\mat{D}}\mat{D}))\mat{F}.
\end{align}
The parameter $\alpha$ allows us to smoothly vary the weighting of the source and destination behaviors. Source-only behavior is given by $\alpha=0$; destination-only by $\alpha=1$; to weight source and destination equally, take $\alpha=\nicefrac{1}{2}$.

### 2008-06-14 tables/traffic_models.tex
More work on appearance of models table.

\begin{table*}
\begin{center}
\small
\begin{tabular}{|c|c|l|}
\multicolumn{1}{c}{\textbf{model}} &
\multicolumn{1}{c}{\textbf{transformation}} &
\multicolumn{1}{c}{\textbf{description}} \\
\hline
\caps{GMM} &
--- &
the general matrix model
\\\hline\hline
time uniform &
$\mat{A}'=\mat{A}(\ones/d_t)$ &
all start times are equally likely
\\\hline
node uniform &
$\mat{S}'=\mat{S}(\ones/n)$~~~~$\mat{D}'=\mat{D}(\ones/n)$ &
nodes behave stochastically identically with respect to flows
\\\hline
full uniform &
\textit{all uniform transformations} &
applies all the uniformity assumptions of the above models
\\\hline\hline
time marginal &
$\mat{A}'=(\ones/f)\mat{A}$ &
start times chosen from marginal distribution of start times
\\\hline
size marginal &
$\mat{B}'=(\ones/f)\mat{B}$ &
flow size (bytes) is chosen independently of other properties
\\\hline
node marginal &
$\mat{S}'=(\ones/f)\mat{S}$~~~~$\mat{D}'=(\ones/f)\mat{D}$ &
nodes behave distinctly, but behavior is independent of flows
\\\hline
packet marginal &
$\mat{Z}'=(\ones/f)\mat{Z}$~~~~$\mat{V}'=(\ones/f)\mat{V}$ &
packet behavior is variable bit-rate, aggregated across all flows
\\\hline
full marginal &
\textit{all marginal transformations} &
applies all the marginality assumptions of the above four models
\\\hline\hline
source conditional &
$\mat{F}'=(\trans{\mat{SS}}/f)\mat{F}$ &
flow behaviors are aggregated on a per source-node basis
\\\hline
dest conditional &
$\mat{F}'=(\trans{\mat{DD}}/f)\mat{F}$ &
flow behaviors are aggregated on a per destination-node basis
\\\hline
mixed conditional &
$\mat{F}'=\frac{1}{2f}(\trans{\mat{SS}}+\trans{\mat{DD}})\mat{F}$ &
flow behaviors are aggregated on a mixed source/destination basis
\\\hline
\end{tabular}
\caption{Matrix-based traffic models evaluated by paired differential simulation.}
\label{tab:traffic-models}
\end{center}
\vspace{-2em}
\end{table*}

>>>>

\begin{table*}
\begin{center}
\small
\begin{tabular}{|c|c|l|}
\multicolumn{1}{c}{\textbf{model}} &
\multicolumn{1}{c}{\textbf{transformation}} &
\multicolumn{1}{c}{\textbf{description}} \\
\hline
\caps{GMM} &
--- &
the general matrix model
\\\hline\hline
time uniform &
$\mat{A}' = (\nicefrac{1}{n})\,\mat{A}\ones$ &
all start times are equally likely
\\\hline
node uniform &
$\mat{S}' = (\nicefrac{1}{n})\,\mat{S}\ones \quad
 \mat{D}' = (\nicefrac{1}{n})\,\mat{D}\ones$ &
all nodes equally likely as source or destination
\\\hline
full uniform &
\textit{all uniform transformations} &
all start times, sources and destinations equally likely
\\\hline\hline
time marginal &
$\mat{A}' = (\nicefrac{1}{f})\,\ones\mat{A}$ &
start times chosen from marginal distribution of start times
\\\hline
size marginal &
$\mat{B}' = (\nicefrac{1}{f})\,\ones\mat{B}$ &
flow size (bytes) is chosen independently of other properties
\\\hline
node marginal &
$\mat{S}' = (\nicefrac{1}{f})\,\ones\mat{S} \quad
 \mat{D}' = (\nicefrac{1}{f})\,\ones\mat{D}$ &
nodes behave distinctly, but behavior is independent of flows
\\\hline
packet marginal &
$\mat{Z}' = (\nicefrac{1}{f})\,\ones\mat{Z} \quad
 \mat{V}' = (\nicefrac{1}{f})\,\ones\mat{V}$ &
packet behavior is variable bit-rate, aggregated across all flows
\\\hline
full marginal &
\textit{all marginal transformations} &
applies all the marginality assumptions of the above four models
\\\hline\hline
source conditional &
$\mat{F}' = \rStoch(\trans{\mat{S}}\mat{S})\,\mat{F}$ &
flow behaviors are aggregated on a per source-node basis
\\\hline
dest conditional &
$\mat{F}' = \rStoch(\trans{\mat{D}}\mat{D})\,\mat{F}$ &
flow behaviors are aggregated on a per destination-node basis
\\\hline
mixed conditional &
$\mat{F}' = \nicefrac{1}{2}\,(
              \rStoch(\trans{\mat{S}}\mat{S}) +
              \rStoch(\trans{\mat{D}}\mat{D})
            )\,\mat{F}$ &
flow behaviors are aggregated on a mixed source/destination basis
\\\hline
\end{tabular}
\caption{Matrix-based traffic models evaluated by paired differential simulation.}
\label{tab:traffic-models}
\end{center}
\vspace{-1em}
\end{table*}
